Rotations and Insecticide Resistance initial plots

### 2017-11-21 inst/documents/rotations1.Rmd
max_generations -> max_gen

# TODO remove hardcode fitnesses from here
dfr <- run_rot(rotation_interval=50, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.01)

@@

dfr <- run_rot(rotation_interval=50, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.001)

@@

dfr <- run_rot(rotation_interval=0, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, expo_hi=0.5, migration=0.01)

@@

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0 )

>>>>

# TODO remove hardcode fitnesses from here
dfr <- run_rot(rotation_interval=50, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.01)

@@

dfr <- run_rot(rotation_interval=50, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.001)

@@

dfr <- run_rot(rotation_interval=0, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, expo_hi=0.5, migration=0.01)

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0 )

### 2017-11-21 inst/documents/rotations_notes.Rmd
max_generations -> max_gen

df_results <- data.frame(generation=1:max_generations,
                         insecticide=NA,
                         r1_active=NA,
                         r1_refuge=NA,
                         r2_active=NA,
                         r2_refuge=NA,
                         r3_active=NA,
                         r3_refuge=NA,
                         r4_active=NA,
                         r4_refuge=NA, stringsAsFactors = FALSE)

@@

# create inflexible columns ready to add r* columns on
max_generations <- 10
df_results <- data.frame(generation=1:max_generations,
                         insecticide=NA)

@@

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0 )

@@

n_insecticides    | 3,4,5
max_generations   | 
rotation_interval | 5 - 50 (integer)
male_expo_prop    | 0 - 1
coverage          | 0.1 - 0.9
migration         |  
cost              | 0 - 0.05

@@

#high cost, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )

@@

RAF <- set_start_freqs(n=3, max_generations = 1, freqs=c(0.1,0.01,0.001))
RAF2 <- set_start_freqs(n=3, max_generations = 1, freqs=c(1,2,3))

>>>>

df_results <- data.frame(generation=1:max_gen,
                         insecticide=NA,
                         r1_active=NA,
                         r1_refuge=NA,
                         r2_active=NA,
                         r2_refuge=NA,
                         r3_active=NA,
                         r3_refuge=NA,
                         r4_active=NA,
                         r4_refuge=NA, stringsAsFactors = FALSE)

@@

# create inflexible columns ready to add r* columns on
max_gen <- 10
df_results <- data.frame(generation=1:max_gen,
                         insecticide=NA)

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0 )

@@

n_insecticides    | 3,4,5
max_gen   | 
rotation_interval | 5 - 50 (integer)
male_expo_prop    | 0 - 1
coverage          | 0.1 - 0.9
migration         |  
cost              | 0 - 0.05

@@

#high cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )

@@

RAF <- set_start_freqs(n=3, max_gen = 1, freqs=c(0.1,0.01,0.001))
RAF2 <- set_start_freqs(n=3, max_gen = 1, freqs=c(1,2,3))
